### 2021-08-13 paper/paper.tex
small edits to Section 3.1

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal magnetohydrodynamics (MHD) equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used for the purpose of demonstrating the high-order accuracy and convergence properties
of the frameworks.

@@

To assess the performance of the two codes, we vary the polynomial degree
(\lstinline{polydeg}) from 3 to 15.
This corresponds to considering DG approximations of increasing spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of Runge-Kutta stages per time step for the selected time-stepping method. In other words, the PID acts
as a metric for the run time required for the right hand side (RHS) evaluation of each DOF.

>>>>

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal magnetohydrodynamics (MHD) equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used to demonstrate the high-order accuracy and convergence properties
of the frameworks.

@@

To assess the performance of the two codes, we vary the polynomial degree
(\lstinline{polydeg}) from 3 to 15.
This corresponds to considering DG approximations of increasing spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of Runge-Kutta stages per time step for the selected time-stepping method. In other words, the PID
measures the run time required for the right hand side (RHS) evaluation of each DOF.
